### 2024-04-15 acronyms/acronyms.tex
global acronyms file
acronyms
hazop

\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}

@@

\newacronym{ics}{ICS}{Industrial Control System}

@@

\newacronym{bol}{BOL}{beginning-of-life}
\newacronym{eol}{EOL}{end-of-life}
\newacronym{mol}{MOL}{middle-of-life}

@@

\newacronym{dc}{DC}{direct-current}
\newacronym{ac}{AC}{alternating-current}

@@

\newacronym{usa}{US}{United States}

@@

\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
\newacronym{doe}{DOE}{Department of Energy}

@@

\newacronym{pcap}{PCAP}{packet capture file}

@@

\newacronym{haz}{HAZOP}{hazard and operability analysis}

>>>>

@@

@@

@@

@@

@@

@@

@@

\newacronym{haz}{HAZOP}{Hazard and Operability Analysis}
\newacronym{onr}{ONR}{Office of Naval Research}
\newacronym{ui}{UI}{University of Idaho}
\newacronym{isu}{ISU}{Idaho State University}
\newacronym{bsu}{BSU}{Boise State University}
\newacronym{skp}{SKP}{Senior Key Personnel}
\newacronym{bpc}{BPC}{Broadening Participation in Computing}
\newacronym{epi}{EPI}{Energy Policy Institute}
%\newacronym{}{}{}
